Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-21 Paper.tex
Add regulation contribution

@@

\bibitem{Coinbase19} Coinbase. Intercambio de moneda digital \href{https://www.coinbase.com/price/ethereum}{https://www.coinbase.com/price/ethereum}
\bibitem{ConsenSys19} Ethereum Smart Contract Best Practices. Security tools. ConsenSys. 12 Agosto 2019.
\bibitem{Docker19} Docker Documentation. How nodes work. 6 Septiembre 2019.  \href{https://docs.docker.com/engine/swarm/how-swarm-mode-works/nodes/}{Docker Swarm}
\bibitem{ETHBerlinZwei19} Hackathon ETH Berlín Zwei. Twitter. 6 Septiembre 2019. \href{https://twitter.com/ETHBerlin}{https://twitter.com/ETHBerlin}
\bibitem{Hegedus18} P. Hegedus. "Towards Analyzing the Complexity Landscape of Solidity Based Ethereum Smart Contracts". 2018 IEEE/ACM 1st International Workshop on Emerging Trends in Software Engineering for Blockchain (WETSEB). 27 Mayo-3 Junio 2018. \href{https://ieeexplore.ieee.org/document/8445056}{https://ieeexplore.ieee.org/document/8445056}
\bibitem{MakerDAO19} MakerDAO. Stability for the blockchain.  \href{https://makerdao.com/en/dai}{https://makerdao.com/en/dai}
\bibitem{Munoz18} J. L. Muñoz. "Docker Containers". Apuntes de las clases magistrales. Máster en Tecnologías Blockchain. 1, Edición. UPC School. 29 Noviembre 2018.
\bibitem{Nakamoto08} S. Nakamoto. "Bitcoin: A Peer-to-Peer Electronic Cash System". 31 Octubre 2008.  \href{https://bitcoin.org/bitcoin.pdf}{https://bitcoin.org/bitcoin.pdf}
\bibitem{RaspberryPi19} Raspberry Pi 3 Modelo B - Placa Base (1,2 GHz Quad-Core Arm Cortex-A53, 1 GB RAM, USB 2.0). Amazon. 11 Agosto 2019.
\bibitem{RaspberryPiBuy19} Raspberry Pi FAQs. BUYING AND SHIPPING. Where can I buy a Raspberry Pi?. Página Web oficial. 11 Agosto 2019.  \href{https://www.raspberrypi.org/help/faqs/#buyingWhere}{https://www.raspberrypi.org/help/faqs/\#buyingWhere}
\bibitem{Stallings04} W. Stallings. "Comunicaciones y redes de computadores". 1 Septiembre 2004. Páginas 904. Pearson Prentice Hall. ISBN-13: 978-8420541105.
\end{thebibliography}
\clearpage

>>>>

\section{Regulation status}
\vspace{0.35cm}

Any organisation that has customers on the premises,
from coffee shops to libraries, might want to offer free (or even
paid-for) Wi-Fi as an attraction. Collecting and storing personal
information brings responsibilities under European Union’s General
Data Protection Directive (GDPR). The GDPR\cite{gdpr16}, which took
effect on 25 May 2018, applies to any organisation that handles EU
residents’ personal data. From 25 May on, however, organisations
failing to comply with the regulation face fines of up to 4 \% of
their global turnover. There are Certified EU General Data Protection
Regulation Foundation (GDPR) Training Courses.

We take another look at the major obligations imposed by this
regulation\cite{tata17}:

\vspace{0.35cm}
1. ART 5/1B and 1C - DATA MINIMISATION:
Prohibited is the collection of more data than that required for the
adequate purposes for which it is being processed. For instance, if
you offer restaurant guests free WiFi access it is not necessary to
ask for their address data in this connection. However, if you are
interested in finding out where your guests are from - which can be a
completely legitimate interest for a restaurant owner to have - you
are indeed entitled to pose the question, but your guests must divulge
the information consciously and voluntarily and perhaps you should
only ask them for their postcode.

\vspace{0.35cm}
2. ART 5/1E - STORAGE LIMITATION:
Data may not be stored for longer than is necessary for the purposes
for which the data is being processed or than is necessary to meet
legal requirements.

\vspace{0.35cm}
3. ART 5/1A - LAWFUL, FAIR AND TRANSPARENT DATA
PROCESSING: Data subjects have a right to know what their data is
being used for and must be able to rely on the fact that it will not
be used for other purposes. This is why coupling of information is
prohibited. Collected data may only be used for the agreed purpose –
for example, to allow restaurant guests to use the in-house
WiFi. Hence, the coupling of the provision of WiFi access to a
compulsory subscription to a newsletter is no longer permitted. You
are naturally permitted to invite your guests to subscribe – but you
will need to do so separately and in an obvious manner.

\vspace{0.35cm}
4. ART 5/2
and 30 - ACCOUNTABILITY AND RECORDS: The GDPR requires that everyone
dealing with personal data must maintain records of the processing of
this data and be able to demonstrate that the corresponding processing
activities conform to legal requirements. Hence, they must document in
a data processing register which categories of data are collected from
which categories of person and how the data is processed. Are you
processing the data in-house or is the task outsourced to a service
provider? Is data transferred to a country outside of the EU? If so,
does the destination country provide a level of data protection
equivalent to that in the EU? This is perhaps the most problematic
aspect because even if you outsource processing or use a Cloud service
provider you are still held responsible for ensuring legal compliance
with regard to what happens to any data obtained from subjects.

\vspace{0.35cm}
5. ART 5/1F and 28 - INTEGRITY AND CONFIDENTIALITY: You must ensure
appropriate security of data and also ensure that it cannot be
tampered with. But how do you do that? What if hackers launch a
malicious attack? Don’t worry; even government websites are not immune
to this sort of thing and it would be hardly fair if the GDPR were to
impose more stringent requirements on you. However, you are required
to put appropriate technical or organisational measures in place that
provide adequate protection of your customers’ data. The GDPR does not
spell out in so many words what these required ‘measures’
are. However, you can be certain that you will be at least be expected
to have a valid SSL certificate for your data-collecting website and
to conclude instruction and confidentiality agreements with your
personnel who come into contact with the corresponding data.

\vspace{0.35cm}
6. ART
12, 13 and 15 - INFORMATION AND RIGHT OF ACCESS: You are obligated to
provide information at any time to data subjects whose data you
process. This information and your data privacy policy must be written
in clearly comprehensible language and include a contact option for
data subjects.

In addition, the Proposal for a new ePrivacy
Regulation was tabled in January 2017, when GDPR was not yet
applicable and the European Electronic Communications Code\cite{eecc18}
was still being negotiated. Now, GDPR has been implemented,
changing many of the approaches and behaviours that the ePrivacy
Regulation aims to tackle. Additionally, the new EECC already ensures
an extended definition of what an e-communications service is, thereby
achieving one of the purported goals of the ePrivacy Regulation, which
is to broaden the scope of application of confidentiality obligations
to a larger number of Internet-based players.

\vspace{0.35cm} Because of these issues, good advice for anyone
planning to set up a hotspot would be to collect as little personal
data from users as possible, and to think of any additional collection
as a potential liability.

@@

\bibitem{Coinbase19} Coinbase. Intercambio de moneda digital \href{https://www.coinbase.com/price/ethereum}{https://www.coinbase.com/price/ethereum}
\bibitem{ConsenSys19} Ethereum Smart Contract Best Practices. Security tools. ConsenSys. 12 Agosto 2019.
\bibitem{Docker19} Docker Documentation. How nodes work. 6 Septiembre 2019.  \href{https://docs.docker.com/engine/swarm/how-swarm-mode-works/nodes/}{Docker Swarm}
\bibitem{ETHBerlinZwei19} Hackathon ETH Berlín Zwei. Twitter. 6 Septiembre 2019. \href{https://twitter.com/ETHBerlin}{https://twitter.com/ETHBerlin}
\bibitem{Hegedus18} P. Hegedus. "Towards Analyzing the Complexity Landscape of Solidity Based Ethereum Smart Contracts". 2018 IEEE/ACM 1st International Workshop on Emerging Trends in Software Engineering for Blockchain (WETSEB). 27 Mayo-3 Junio 2018. \href{https://ieeexplore.ieee.org/document/8445056}{https://ieeexplore.ieee.org/document/8445056}
\bibitem{MakerDAO19} MakerDAO. Stability for the blockchain.  \href{https://makerdao.com/en/dai}{https://makerdao.com/en/dai}
\bibitem{Munoz18} J. L. Muñoz. "Docker Containers". Apuntes de las clases magistrales. Máster en Tecnologías Blockchain. 1, Edición. UPC School. 29 Noviembre 2018.
\bibitem{Nakamoto08} S. Nakamoto. "Bitcoin: A Peer-to-Peer Electronic Cash System". 31 Octubre 2008.  \href{https://bitcoin.org/bitcoin.pdf}{https://bitcoin.org/bitcoin.pdf}
\bibitem{RaspberryPi19} Raspberry Pi 3 Modelo B - Placa Base (1,2 GHz Quad-Core Arm Cortex-A53, 1 GB RAM, USB 2.0). Amazon. 11 Agosto 2019.
\bibitem{RaspberryPiBuy19} Raspberry Pi FAQs. BUYING AND SHIPPING. Where can I buy a Raspberry Pi?. Página Web oficial. 11 Agosto 2019.  \href{https://www.raspberrypi.org/help/faqs/#buyingWhere}{https://www.raspberrypi.org/help/faqs/\#buyingWhere}
\bibitem{Stallings04} W. Stallings. "Comunicaciones y redes de computadores". 1 Septiembre 2004. Páginas 904. Pearson Prentice Hall. ISBN-13: 978-8420541105.

\bibitem{berec16} Report on OTT services. BEREC (Body of European Regulators for Electronic Communications). January 2016.
\bibitem{eecc18} [EECC 18] Directive (EU) 2018/1972 of the European
  Parliament and of the Council of 11 December 2018 establishing the
  European Electronic Communications Code (Recast)Text with EEA
  relevance. PE/52/2018/REV/1.

\bibitem{gdpr16} [GDPR 16] Regulation (EU) 2016/679 of the European
  Parliament and of the Council of 27 April 2016 on the protection of
  natural persons with regard to the processing of personal data and
  on the free movement of such data, and repealing Directive 95/46/EC
  (General Data Protection Regulation) (Text with EEA relevance).

\bibitem{h202018} [H2020 18] Ethics and data protection. European
  Commission (DG Research and Innovation). 14 November 2018.

\bibitem{tata17} [Tata 17] A Systematic Approach to Ensuring GDPR
    Compliance: Key Action Items for Telecom Operators. White
    Paper. Tata Consultancy Services. 2017.

\end{thebibliography}
\clearpage
